imputation_stickle

### 2023-05-01 R/stickle_imputation_error_bars.Rmd

stick

@@

M = 5
k = 5
stick_matrix <- matrix(NA, nrow=nrow(extant_stickle), ncol = M)
set.seed(12)
fold <- sample(1:k, size = nrow(extant_stickle), replace=TRUE)
for(i in 1:k){
extant_stickle_temp <- extant_stickle
extant_stickle_temp$gender[fold==i] <- NA
imputed_stick <- mice(extant_stickle_temp,m=M)
for(n in 1:M){

  complete_stick <- complete(imputed_stick, n)

  complete_stick$gender[fold==i]
  stick_matrix[fold==i, n] <- as.character(complete_stick$gender[fold==i])
}

}
pct_male <- apply(stick_matrix,1,function(x){
  mean(x == "Male")
})

imptest <- data_frame(truth = as.factor(extant_stickle$gender), pct_male)
roc_pred <- prediction(imptest$pct_male, imptest$truth)

auc_rocr <- performance(roc_pred, measure="auc")
plot(performance(roc_pred, measure="tpr", x.measure="fpr"))

auc_rocr@y.values[[1]]

@@

```{r}
#getting time vector, adding it to imputed data
univ <- stick %>% 
  mutate(time = as.integer(sub(".*([0-9]{2})\\..*", "\\1",univID)))
times <- univ %>% drop_na(time) %>% pull(time)

times_vector <- c(rep(1,43)) %>% 
  append(21-times)
```

@@

>>>>

stick_whole <- stick %>% select(-c(univID, ips))

@@

@@

```{r}
#getting time vector, adding it to imputed data
univ <- stick %>% 
  mutate(time = as.integer(sub(".*([0-9]{2})\\..*", "\\1",univID)))
times <- univ %>% drop_na(time) %>% cut(time, breaks = 1,3,5,7,9,11,13,15,17) pull(time)

cut(times, breaks = 8, labels = c(8,7,6,5,4,3,2,1))
times_vector <-length(rep(c(1,2,3,4,5,6,7,8,9),each=86))
cut(times_vector, breaks=2, labels)

help(cut)
```

@@

```{r}
#Using MICE imputation to get imputed datasets (function)

impute_stickledata <- function(M, dataset){
  imputed_stick_ <- mice(dataset,m=M)
  complete_stick_list <- list()
  for(m in 1:M){
    complete_stick_list[[m]] <- complete(imputed_stick_, m)
  }
  return(complete_stick_list)
}

```
```{r}
# My debugging process. Found out about enquo() and !!, which allows for inputting variables within a function.
# pretty, pretty cool

# test_ <- function(M,variable,data){
#   variable <- enquo(variable)
#   temp_comp_lists <- list()
#   est_list <- list()
#   for(m in 1:M){
#   temp_comp_lists[[m]] <- data[[m]][-c(1:367),]
#   temp_comp_lists[[m]]$time <- times_vector
#   
#   
#   est_list[[m]] <- temp_comp_lists[[m]] %>% group_by(gender, time) %>% summarize(xbar = mean(!! variable), se = sqrt(var(!! variable)/n()), n())
#   est_list[[m]]$imp = m
#   }
#   return(est_list)
# }
# 
# testing_ <- impute_stickledata(5,stick_whole)
# test_(5, stl, testing_)

```{r}
completed_stick_lists <- impute_stickledata(5,stick_whole)
#doing the grouping and summarizing for all imputed datasets function
imputed_means <- function(M,target_variable){
target_variable <- enquo(target_variable)

temp_comp_lists <- list()
est_list <- list()

# completed_stick_lists <- impute_stickledata(M,stick_whole). I could leave this in here but don't necessarily need it
for(m in 1:M){

temp_comp_lists[[m]] <- completed_stick_lists[[m]][-c(1:367),]
temp_comp_lists[[m]]$time <- times_vector

est_list[[m]] <- temp_comp_lists[[m]] %>% group_by(gender, time) %>% summarize(xbar = mean(!! target_variable), se = sqrt(var(!! target_variable)/n()), n())
est_list[[m]]$imp = m
}

# stacking the datasets
combined_est <- do.call(rbind,est_list)
return(combined_est)
}

```{r}
#Function for combined SE
combined_se_function <- function(M, variable){
variable <- enquo(variable)
combined_estimate <- imputed_means(5, !! variable)

combined_est_errors <- combined_estimate %>% group_by(gender, time) %>% summarize(x_bar_bar  = mean(xbar), B_m = var(xbar), W_m = mean(se^2), se_xbar_bar = sqrt(W_m+(1+1/5)*(B_m)), r = (1+1/5)*B_m/W_m, U = (5-1)*(1+(1/r)^2), t_val = qt(0.05/2, df = U, lower.tail = FALSE), uci = x_bar_bar + t_val * se_xbar_bar, lci = x_bar_bar - t_val * se_xbar_bar, t_se = t_val * se_xbar_bar)

return(combined_est_errors)
}

combined_se_function(5, stl)

```{r}
#function for ggplot of desired var
stickle_imputation_plotting <- function(M, var){
  v <- as.character(substitute(var))
  var =enquo(var)
  string = paste("mean of ", v)
  combined_errors <- combined_se_function(5, !! var)

  bb<- ggplot(data= combined_errors, aes(x = time, y = x_bar_bar, col = gender))+geom_point()+geom_line() +   geom_errorbar(aes(ymin = lci, ymax = uci, group = gender),
     width = 0.2)+ labs(x = "Time", y = string)

  return(bb)
}
stickle_imputation_plotting(5,stl)
